%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Rambod Rahmani Curriculum Eng
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\usepackage{changepage}
\usepackage{csquotes}
\hypersetup{colorlinks=true,urlcolor={blue}}
\def\UrlBreaks{\do\/\do-}

\begin{document}

\header{Rambod}{Rahmani}{Student at University of Pisa} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION 1
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
Via Pietro Casu, 16
Sassari, (SS) 07100
Italy
~
(+39) 333 3840979
(+39) 079 2859049
~
\small{\href{mailto:rambodrahmani@yahoo.it}{{\addfontfeature{Color=blue}rambodrahmani@yahoo.it}}}
\small{{\faGlobe}}~\href{http://rambodrahmani.it}{{\addfontfeature{Color=blue}rambodrahmani.it}}\vspace{6mm}
\section{Languages}
Persian (Mother tongue)
Italian (Mother tongue)
English (C1)
French (A2)
Spanish (A1)\vspace{6mm}
\section{Programming \small{\textcolor{magenta}{{\faHeart}}}}
Java, JavaFX, Python, C, C++, Objective-C, .NET Framework, R, Latex, OpenCV, APEX, SQL, PL/SQL, MySQL, PHP, CSS, JavaScript, jQuery, HTML5, Django, XML, GWT, JSON, Shell Script.\vspace{6mm}
\section{Software}
xCode, Android Studio, Windows Phone SDK, Matlab, Visual Studio, Eclipse, Photoshop, Illustrator, Dreamweaver, Premiere Pro, VirtualBox, , ISPConfig, Openstack, Puppet, OpenMediaVault, MongoDB, Metasploit, Wireshark, Git, Jira, Trac.\vspace{6mm}
\section{Hardware}
Arduino, Raspberry Pi, Embedded Pi, Cubieboard, Torobot, TP-Link CPE210, CPE510, EAP225, Ubiquiti Nanostation M3 and Picostation.
\end{aside}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\section{Summary}
\vspace{-3mm}
I was born in Iran in 1993 and moved to Italy at the age of 7. I started studying programming languages at the age of 15 and began to work as a freelance programmer a couple of years later. At the age of 19 I was admitted at the University of Pisa as a Computer Science Student and I am currently studying for my last exams. In the last four years, beside studying for my examinations, I worked for IT Companies and for the Italian government, I took part in group projects and tried to startup my own ideas. During the academic year 2016/2017, my goals have shifted. I have developed a deep interest in Quantum Physics and its applications to computer science: I am hoping to pursue an academic career in Quantum Computer Science.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\vspace{-3mm}
\begin{entrylist}
%------------------------------------------------
\entry
{2013 - 2017}
{Bachelor {\normalfont\small{of Engineering Studies - Computer Science}}}
{University of Pisa, Italy}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{2008 - 2013}
{High School Diploma {\normalfont\small{100/100 - Scientific Lyceum}}}
{Scientific Lyceum "G. Spano", Italy}
{\vspace{-5mm}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PERSONAL STUDIES SECTION
%----------------------------------------------------------------------------------------

\patchcmd{\entry}{11.8cm}{14.8cm}{}{}
\section{Personal Studies}
\vspace{-3mm}
\emph{\small{The following is a list of in-depth courses which I followed during my Bachelor of Engineering.}}

\begin{entrylist}
%------------------------------------------------
\entry
{}
{Complete Java Masterclass: {\normalfont\small{Learn to master Java 8 core development.}}}
{Tim Buchalka}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Learning JavaFX GUI Development: {\normalfont\small{Develop enterprise apps using JavaFX.}}}
{Peggy Fisher}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Python 3 and Django Full Stack Web Developer Bootcamp{\normalfont\small{.}}}
{Jose Marcial Portilla}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Advanced C++ Programming: {\normalfont\small{Intermediate to advanced C++, including C++ 11's additions.}}}
{John Purcell}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Machine Learning: Hands-On Python \& R In Data Science{\normalfont\small{.}}}
{Kirill Eremenko, Hadelin de Ponteves}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Introduction to Computer Vision | Master OpenCV 3 in Python{\normalfont\small{.}}}
{Rajeev Ratan}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{The Web Developer Bootcamp: {\normalfont\small{HTML, CSS, JS, jQuery, Node.js, MongoDB.}}}
{Colt Steele}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Oracle DBA 11g/12c - Database Administration for Junior DBA{\normalfont\small{.}}}
{Amarnath Reddy}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Thoughtful Web Development: {\normalfont\small{HTML5, CSS3, JavaScript, jQuery, Vue.js, AJAX, PHP.}}}
{OnlyKiosk Tech}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Complete Ethical Hacking Course: {\normalfont\small{SSL Strip, BruteForcing, DDoS, Reverse Shells.}}}
{Ermin Kreponic}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{The Complete Networking Fundamentals Course: {\normalfont\small{Start your journey to CCNA.}}}
{David Bombal}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Cisco Networking Fundamentals: {\normalfont\small{Complete Cisco IT Networking Fundamentals course.}}}
{Keith Gebhardt}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Mysteries of Modern Physics: Time{\normalfont\small{.}}}
{Professor Sean Carroll, Ph.D.}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{The Higgs Boson and Beyond{\normalfont\small{.}}}
{Professor Sean Carroll, Ph.D}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Understanding Modern Electronics{\normalfont\small{.}}}
{Professor Richard Wolfson, Ph.D}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Thermodynamics: Four Laws That Move the Universe{\normalfont\small{.}}}
{Professor Jeffrey C. Grossman, Ph.D}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Quantum Mechanics{\normalfont\small{.}}}
{Professor Benjamin Schumacher, Ph.D}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Physics and Our Universe{\normalfont\small{.}}}
{Professor Richard Wolfson, Ph.D}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Impossible: Physics Beyond the Edge{\normalfont\small{.}}}
{Professor Benjamin Schumacher, Ph.D}
{\vspace{-3mm}}
%------------------------------------------------
\entry
{}
{Black Holes, Tides, and Curved Spacetime: Understanding Gravity{\normalfont\small{.}}}
{Professor Benjamin Schumacher, Ph.D}
{\vspace{-3mm}}
%------------------------------------------------
\end{entrylist}

\clearpage

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION 2
%----------------------------------------------------------------------------------------

\begin{aside}\vspace{-2.75cm}
\section{Operating Systems}
Windows 7/8/10, Mac OS X, iOS, Android, Debian, Linux Mint, Arch Linux, Raspbian, OpenWRT, Kali Linux, Parrot OS, Tails.\vspace{6mm}
\section{Linkedin \textcolor{blue}{\faLinkedinSquare}}
For full and detailed information regarding my work experience, projects and awards please refer to my \textbf{Linkedin Profile}: \href{http://it.linkedin.com/in/rambodrahmani}{{\addfontfeature{Color=blue}it.linkedin.com/in/}}\\\href{http://it.linkedin.com/in/rambodrahmani}{{\addfontfeature{Color=blue}rambodrahmani}}.\vspace{6mm}
\section{GitHub \textcolor{teal}{\faGithub}}
\emph{"It’s called stealing or piracy, as if sharing a wealth of knowledge were the moral equivalent of plundering a ship and murdering its crew.\\But sharing isn’t immoral - it’s a moral imperative.\\Only those blinded by greed would refuse to let a friend make a copy."}\vspace{1mm}
\textbf{GitHub Profile}: \href{http://github.com/rambodrahmani}{{\addfontfeature{Color=blue}github.com/}}\\\href{http://github.com/rambodrahmani}{{\addfontfeature{Color=blue}rambodrahmani}}.\vspace{6mm}
\section{Academia.edu \textcolor{orange}{\faUniversity}}
For full and detailed information regarding my personal studies please refer to my \textbf{Academia.edu Profile}: \href{http://pisa.academia.edu/RambodRahmani}{{\addfontfeature{Color=blue}pisa.academia.edu/}}\\\href{http://pisa.academia.edu/RambodRahmani}{{\addfontfeature{Color=blue}RambodRahmani}}.\vspace{6mm}
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\patchcmd{\entry}{14.8cm}{11.8cm}{}{}
\section{Work Experience}
\vspace{-3mm}
\begin{entrylist}
%------------------------------------------------
\entry
{2013 - 2016}
{Presidency of the Council of Ministers - Department of Information for Security}
{Italy}
{\emph{Italian Government - IT Analyst} \\
I was recruited by Presidency of the Council of Ministers of Rome during the second semester of my first year at University of Pisa. I worked in several Italian cities for more than 2 years. I was involved in both software development and malware analysis for the  Department of Information for Security.}
%------------------------------------------------
\entry
{2013 - 2016}
{System Administrator}
{Rambod Rahmani}
{I was involved in in-home Server Setup as part of our self-educating projects at EigenLab. Additionally I spent a great deal of time working on both dedicated servers and VPS (OS Installation, ISPConfig Setup and maintenance). The majority of my experiences as SysAdmin was focused on Linux Servers.}
%------------------------------------------------
\entry
{2014-2015}
{Boccaccio Club}
{Pisa, Italy}
{\emph{Software Programmer} \\
Boccaccio Club iOS and Android App Development. Wireless Network Routing with Multiple Access Points: internet access is guaranteed only when the Boccaccio Club App is installed on your device. In order to achieve such an advanced authentication method I developed a custom captive portal named DYNAMO.}
%------------------------------------------------
\entry
{2015}
{PHOS Project}
{University of Pisa}
{\emph{Software Programmer} \\
iOS and Android App development for PHOS Project (Aerospace project at University of Pisa part of the REXUS/BEXUS programme).}
%------------------------------------------------
\entry
{2013}
{Ciclope: Raspberry Pi based Humanoid}
{Rambod Rahmani, Giacomo Taormina}
{\emph{Software Development \& Hardware Assembly} \\
Ciclope is a Humanoid robot with the ability to see and analyse the external world using a camera. Its structure has up to 17 degrees of freedom.\\
It is a one-of-a-kind combination of Software and Hardware: it combines the latest OpenCV libraries and the RPi on board camera. I coded basic functionalities such as object-tracking and face-recognition, and its control interface using Python, C and C++.}
%------------------------------------------------
\entry
{2013}
{Ambulatory Proctology Office}
{Sardinia, Italy}
{\emph{Software Programmer} \\
I developed a software named "Anamnesi" (Objective-C - MAC OS X) used to manage patients medical histories. Each patient is identified using his fiscal code and the ambulatory doctors are able to access all medical histories stored on a server wherever they are.}
%------------------------------------------------
\entry
{2012}
{MALIBU Village}
{Canet-Plage, Languedoc-Roussillon, France}
{\emph{Internship} \\
I worked as IT Support at MALIBU Village as part of the "Leonardo Project" internship. This was the first time I had a hands-on experience with Ubiquiti Picostations.}
%------------------------------------------------
\entry
{2010 - 2012}
{Italian Navy}
{San Giorgio-class amphibious transport dock, Italy}
{\emph{Software Programmer} \\
I coded a set of three software named \textbf{A.S.C (Acceptance, Sorting and Control)} for the Italian Navy. What started as a late night project to improve my coding skills ended up changing my life for ever when I was still a high school student. During more than two years of daily work I translated a NATO publication made in 2008 into machine language. Thanks to A.S.C. operators do not have to worry anymore about formatting and standardizing their messages: the software checks every line before sending the message and tells the operator how to correct any mistake.}
%------------------------------------------------
\end{entrylist}

\newpage

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION 3
%----------------------------------------------------------------------------------------

\begin{aside}\vspace{-2.75cm}
\section{OpenWRT \textcolor{green}{\faWifi}}
As a member of EigenLab, a local hacklab in Pisa, I was involved in installing and configuring the OpenWRT Distribution on embedded devices that we used to build EigenNet: a local \textbf{Wireless Mesh Network} in the city of Pisa.\vspace{6mm}
\section{Bitcoin \textcolor{red}{\faBitcoin}}
I have been involved in Bitcoins as far as it regards Bitcoin Mining (CGMiner, CPUMiner, USB Miners), Mining Pools, Bitcoin Wallet and Full Bitcoin Node Configuration (Bitcoin Core).\vspace{6mm}
\section{Places \textcolor{light-blue}{\faMapMarker}}
Iran, Italy, Germany, Spain, France, Belgium, Russia.\vspace{6mm}
\small{Last updated: \today\ }
\end{aside}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards, Scholarships and Certificates}
\vspace{-3mm}
\begin{entrylist}
%------------------------------------------------
\entry
{2013 - 2016}
{DSU Scholarship}
{DSU of Tuscany}
{DSU Scholarship by DSU of Tuscany supporting my Bachelor of Engineering Studies.}
%------------------------------------------------
\entry
{2013 - 2016}
{Italian Ministry of Education, University and Research Scholarship}
{MIUR}
{Excellence Scholarship by MIUR supporting my Bachelor of Engineering Studies.}
%------------------------------------------------
\entry
{2012}
{Intel Excellence in Computer Science}
{Intel Corporation}
{Awarded to Rambod Rahmani for developing the A.S.C. Software.}
%------------------------------------------------
\entry
{2012}
{National Excellence Registry}
{Italian Ministry of Education, University and Research}
{Awarded to Rambod Rahmani for developing the A.S.C. Software.}
%------------------------------------------------
\entry
{2012}
{Certificate of Merit}
{Scientific Lyceum "G. Spano", Italy}
{Awarded to Rambod Rahmani for developing the A.S.C. Software.}
%------------------------------------------------
\entry
{2012}
{Europass Mobility Nr. IT/00/2012/859/10}
{}
{Gymnasium Lyceum "D. A. Azuni" and ALFMED (Acad\'emie de Langues France M\'editerran\'ee.).}
%------------------------------------------------
\entry
{2011}
{A.S.C. Software}
{Italian Navy - San Giorgio-class Amphibious Transport Dock}
{Software Development Certificate by the Italian Navy for developing the A.S.C. Software.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PATENTS SECTION
%----------------------------------------------------------------------------------------

\section{Patents}
\vspace{-3mm}
\begin{entrylist}
%------------------------------------------------
\entry
{2015}
{DYNAMO}
{Ministry of Economic Development (Italy) - Request number: 102015000072776}
{Captive portal software which allows for Wi-Fi Access Points to be configured so as to provide internet access only to those devices where a required iOS/Android App is installed. Otherwise the device only has internet access as far as it is needed to install the required App. I developed this custom Captive Portal in order to achieve the advanced authentication method required by Boccaccio Club and thanks to their financial support I was able to patent DYNAMO.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EVENTS SECTION
%----------------------------------------------------------------------------------------

\section{Events}
\vspace{-3mm}
\begin{entrylist}
%------------------------------------------------
\entry
{May 2015}
{International World Wide Web Conference 2015}
{Florence, Italy}
{Research, development, and applications of the topics related to the Web.}
%------------------------------------------------
\entry
{May 2015}
{HEUREKA 2015}
{Berlin, Germany}
{One of the main founders conferences in the German­-speaking world.}
%------------------------------------------------
\entry
{May 2015}
{Berlin Talent Summit 2015}
{Berlin, Germany}
{Europe's leading recruiting conference for high-potentials.}
%------------------------------------------------
\entry
{July 2012}
{9th EXPO-SCIENCES EUROPE 2012 (ESE)}
{Tula, Russia}
{9th MILSET Expo-Sciences Europe (ESE 2012) held in Tula, Russia.}
%------------------------------------------------
\entry
{April 2012}
{I Giovani E Le Scienze 2012}
{Federation of Scientific and Technical Associations}
{The A.S.C. Software was selected as one of the best 30 in the whole country.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}
\vspace{-3mm}
\textbf{Professional:} Startup, Computer Science, Geolocation Systems, Hardware, Smartphones, iOS, Android, Embedded systems, Web development, App development, Software design, Networking, Linux, Hacking, Penetration Testing, Computational Complexity, Artificial Intelligence, Artificial Neural Networks, Computer Vision.\\
\textbf{Personal:} Running, Chess, Cosmology, Astronomical observations, Quantum Computer Science, Physics and Math.

\clearpage

\end{document}